\chapter{Background}

\section{Cryptographic Construction Types}

\subsection{Cryptographic Primitives "Does this go here or under PKC" Public Key}

\subsubsection{Problem solved by PKC}

Public Key Cryptography (PKC) solves the problem of how to enable two people who have never met to but need to communicate securely over insecure channels. 
Public-key uses a one-way function as its public key; this function is easy to compute but hard to invert and is available publicly for use as an encryption method for the key owner. A second key called the private key is known only to the
key owner; this key is a trapdoor function which can invert a ciphertext back to its plaintext form. 

Public-key is bidirectional. The forward direction is the one-way public key which easily computes the ciphertext, the backward direction is the trapdoor private key,
which easily inverts to the plaintext. 
\textbf{insert PKC Diagram}

\subsubsection{Asymmetric & Symmetric Cryptography} 

The concepts of symmetric and asymmetric cryptographic-key schemes are given below as independent forms. However, it is rarely the case that these schemes will be applied in this manner particularly in a Public-key asymmetric system.

\subsubsubsection{Symmetric-key Cryptography} 

In cannonical symmetric-key schemes only one key is generated for both the encryption and decryption algorithms. Symmetric-keys must therefore be exchanged over secure channels where both communicating parties have agreed in advance to the method of
encryption and have exchanged secret keys. 
\newline
Formally, we say the two parties are in possesion of a \textit{shared secret} and each party is mutually, as well as equally responsible for the maintenance of the secret which establishes and secures their communications. 
In certain contexts this method can be made to be as secure as an asymmetric key system its main drawback is the shared secret which has the ability to invalidate the
integrity of communications if either party is compromised.
\newline
Additionally since the method requires a secure channel as well as a
shared secret both parties must know they will have a need for
encrypted communication in advance and negotiate the means of
transmission and key exchange prior to communicating. This means the parties must know each other prior to communicating. 

\subsubsubsection{Asymmetric-key Cryptography}

In contrast symmetric-key schemes are determined by two sets of keys one for each party. Each set consists of a private key known only to the owner and a public key which can be widely distributed. It seems at first glance that asymmetric and symmetric cryptosystems are isolated methods of encryption. However, symmetric
encryption is well-suited for the task of assisting asymmetric key
schemes not only for efficiency purposes but also in the role of key
management. 

\section{Provable Security} 
\textbf{"Should possibly merge this section and the Hardness Assumptions section"} 

\subsection{Defining Security with Games} 

\subsubsection{Semantic Security: Mental Poker and Partial Information} 

Semantic Security was a game proposed by Goldwasser and Micali in their 1982 paper entitled: \textit{"Probabilistic Encryption & How to Play Mental Poker Keeping Secret All Partial Information"} 
\newline
\textbf{Insert Citation: @inproceedings{Goldwasser:1982:PEA:800070.802212, author = {Goldwasser,
Shafi and Micali, Silvio}, title = {Probabilistic Encryption /& How to Play Mental Poker Keeping Secret All Partial Information}, booktitle= {Proceedings of the Fourteenth Annual ACM Symposium on Theory of Computing}, series = {STOC '82}, year ={1982}, isbn = {0-89791-070-2},location = {San Francisco, California, USA}, pages = {365--377},numpages = {13}, url = {http://doi.acm.org/10.1145/800070.802212}, doi
= {10.1145/800070.802212}, acmid = {802212}, publisher = {ACM}, address= {New York, NY, USA}, }} 
\newline
The Mental Poker game was based on the implementation of the Diffie-Hellman implementation of RSA by Rivest, Shamir, Adelman, and Rabin.
\footnote{Specifically, Rabin's 1979 Technical Memo "Digitalized
Signatures and Public-key Functions as Intractable as Factorization""}
\footnote{Rivest, Shamir, and Adelmans paper from Publications of
the ACM, February 1978 "A Method for Obtaining Digital Signatures and
Public Key Cryptosystems."}" 

\textbf{Formal Definition:}
[Gol1982] Proposed the following property for any implementation of a Diffie-Hellman
Public-key Cryptosystem: 
\textit{"An adversary, who knows the encryption of an algorithm and is given the cypher text, cannot obtain any information about the cleartext."} \footnote{[Gol1982] Pg.1, Paragraph 1, Lines 3-6} 
\textbf{Informally:}
A given cryptographic scheme is considered insecure if it is possible for an adversary to recover any information about the plaintext, using the ciphertext, but without knowing the private key. That is, if it is feasible for the adversary to find out some information about the plaintext of the message or recover useful information about the plaintext of the message by manipulating the ciphertext in a reasonable
amount of time, (before he dies of old age or the heat death of the
universe occurs) then the cryptosystem that created those ciphertext
messages (is broke as shit) is insecure. \textit{Kristi fix this wtf dude…}

\subsubsection{Weaknesses in the Assumptions of RSA} 

Goldwasser and Micali pointed out that the security assumptions given in [Riv1978] and [Rab1979] had some particularly significant weaknesses that could not be assumed lightly.
Namely,
\begin{itemize} 
\item Assumption 1: Security of the RSA system is based on the intractability of the number theoretic problems of factorization, index finding, and the decision problem of whether or not a number is a quadratic residue with respect to a composite modulus. 
\item This assumption states that the impossible hardness of one of these problems is
equivalent to RSA being computationally infeasible. 
\item Assumption 2: The second assumption is that there exists a trapdoor function $f(x)$ that is easily computed, while $x$ is not easily computed from $f(x)$ unless some additional information is known. 
\item However, Not all hard problems are as hard as other hard problems. In particular, RSA is based on the assumption that factoring large composites is a hard problem. However, not all large composite numbers are hard to factor in fact some are quite easy. For example, if $c$ is a composite such that $c=qp$ for primes $p$ and $q$ then if $p$ and $q$ are close enough together we have some assurances they will be easily factorable. \textbf{Insert Formal Maths Definition}
\end{itemize} 

\section{Equivalent and Stronger Definitions for Security} 

\textbf{INSERT INTRODUCTORY PARAGRAPH}

\begin{itemize}
\item \textbf{IND-CPA} IND-CPA says if an attacker can choose any plaintext and obtain the corresponding ciphertext, then if the system is secure this information does not help them find the private key. However, the issue with CPA is that it depends on the choices of an adversary who is unaware of the secret key. i.e. If the
attacker has two messages then they have no idea if either one contains the key since they don't know what the key is. 
\item The problem that happens is when I decided to encrypt my own key. Then by CPA I could encrypt the key and the scheme return my key unencrypted and it still satisfies
CPA, and even though the scheme has blatantly revealed my private key, technically it is still semantically secure under CPA (except I am not attacking my own accounts and I had better know my own key). 
\item \textbf{CCAI} 
\item \textbf{CCAII}
\end{itemize}

\section{InfoSec & it's Objectives} 
Their are four basic security objectives that must be considered when constructing any system concerned with securing data or information. The four basic definitions allow for the derivation of all other security objectives which may or may not be
necessary to ensure the security of information for a given system.

\begin{itemize}
\item \textbf{Confidentiality:} The objective of confidentiality ensures that
unauthorized users will not be purposefully or accidentally give access
to the resources protected by a given security system. Integrity:
Ensures that the resources are preserved, used, and appropriately
maintained throughout their life-cycle under the system. That is, any
data is not alterable in an undetectable manner, retains the same
accuracy as its created date (or registered modification date), and is
complete with respect to its creation and activity log. 
\textbf{INSERT TABLE}
\item \textbf{Availability:}
\item \textbf{Non-repudiation:} 

\section{Security Reduction} 

\textbf{Definition}


Hardness Assumptions Average-case We say a
cryptographic algorithm or cryptosystem has average-case hardness if:
Informally: The mathematical problem the algorithm (or system of
algorithms) is based on cannot be solved in polynomial time by a
standard computer with a slightly more than reasonable amount of
resources. More-formally: If a key is chosen at random, then there is
no probabilistic polynomial time algorithm that solves the mathematical
problem for some non negligible probability. Best-case Worst-case For
an average-case security proof we are assured the mathematical problem
the scheme is based on cannot be solved by a classical computer system
in polynomial time in all except a negligible set of its random
functional instances. A worst-case security proof carries all the
security given by the average-case, but it also covers the small set of
functional instances the average-case counts as negligible. Informally,
a worst-case security proof takes the functional instance which is
hardest to solve and shows the scheme is as least as strong as that
instance, and since there are no harder instances, there does not exist
a computer which can solve its mathematical problem in polynomial time.
Post-quantum cryptography The idea of quantum-safe Need for
quantum-safety Schemes with provably secure claims which may or have
been or could be efficient upon implementation Lattice-base
Cryptography Benefits in common with other post-quantum cryptographic
schemes Lattice-based Cryptosystems are a subclass of Post-quantum
cryptosystems. A worst-case security proof for a lattice based scheme
not only claims security against attacks from classical (current)
computer systems, but quantum as well. Drawbacks Not as efficient (yet)
as other more well known schemes. Unique benefit of LBC FHE Fully
Homomorphic Encryption What is FHE Homomorphic Properties of
Cryptographic Schemes Many classical public key cryptography methods
have a homomorphic property, this property says if add two things
together then their sum contains information about those two things.
That is they use successive operations of addition, multiplication,
etc. to create ciphertext. Informal Definition (verbal) Formal
Definition (symbolic) We call these schemes Partially Homomorphic or
Doubly Homomorphic since their operations can be performed
simultaneously. Problem Solved by FHE The problem which FHE solves is
only slightly different than that of PKC. We want to take our encrypted
data, send it to an unauthorized party for processing, and receive the
same results we would get if we had never encrypted it.
- FHE schemes are not limited to a single operation and can
simultaneously compute any number of arbitrary operations. The
cyclotomic field of characteristic two infers so many convenient
structures it is often chosen without consideration to any other ring.
Recent by GCHQ in their own construction, and verified by Peikert
(GATech) in the later part of this year; is that for these rings the
mere guarantee of a short basis reduces the security of the
construction to the easy case, allowing the lattice to be efficiently
decoded, leaving the private key exposed. All cryptographic schemes
such as RSA, El Gamal, etc. must satisfy the requirements of semantic
security, specifically they must satisfy the Indistinguishable Chosen
Plaintext Attack (IND-CPA) requirement. Cryptologists have spent a
great deal of their time removing the natural homomorphisms from most
schemes like RSA. While at the same time wishing for a doubly
homomorphic system. So why would anyone want a doubly homomorphic
encryption system? A doubly homomorphic encryption system would mean I
can use binary to derive boolean logic circuits, if I can do this I can
write any arbitrary program to run on encrypted bits (even Mario Cart).
However, there are situations which can occur where the semantic
security definition is satisfied but an insecurity still occurs. One
such instance is the case where you encrypt your own private key. This
situation is called circular security, and it actually happens pretty
often.
- Define Example Use Cases Cloud Outsourcing Altais Discovery Learning
with Errors (LWE) LWE, has a quantum reduction from SVP. LWE forms the
basis of security for many other algorithms which gain SVP as basis for
their own security. [SV10] is a special case. While ideal rings provide
many benefits due to their structure, the choice of ring is as
important as the choice of base problem. Definition Example Regevs
Hardness Connection Ring LWE The additional application areas and ease
of implementation due to ideal ring structure is convenient, the choice
of ring its self is as important as the problem it is based upon. An
advantage of Ring-LWE is its much smaller set of keys; the ring allows
for more efficient and larger ranges in application areas. Ideal
Lattice-based Cryptography Ideal Ring-LWE allows an even broader range
of applications and efficiency than RLWE due to the additional
structure provided by the principal ideals. Gentrys Scheme "@Gen2009 09
Provides a contrast in terms of efficiency for models following it.
This allows us a convenient way to show the reader how quickly the
research progresses in this area." @Gen2009 First successful
construction fully homomorphic encryption scheme In 2009 Craig Gentry
constructed the first cryptographic system capable of evaluating
arbitrary operations. The scheme was constructed over a principal ideal
lattice @Gen2009 uses a bootstrap method to prove its security.

Definition: Bootstrap Method Smarts Scheme Peikerts Scheme 

Greedy
Problem Management 
Insert Quote by Regev about Principal Ideal Lattice
schemes being greedy 
Discuss Efficiency/Security Balancing

